\documentclass[11pt, a4paper]{resume}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage[a4paper, total={6in, 8in}, margin=0.5in]{geometry}

\name{Paiktra Nom} % Your name
\address{(651)983-3133 \\ \href{paiktranom@gmail.com}{paiktranom@gmail.com} \\ \href{https://paiktranom.github.io}{paiktranom.github.io}}
%=========Summary========

\begin{document}
\begin{rSection}{Summary}
{\normalfont Software engineer with 3 years of experience in providing front-end development, back-end development and application deployment. Proven success in requirements gathering to determine project scope, identify bugs, and put out a product that puts customers first. Experienced in working with Python, HTML, and JavaScript to fulfill project needs. Displays extensive knowledge of agile methodologies, git practices, and developing software solutions.}
\end{rSection}

%========Work Experience=======

\begin{rSection}{Work Experience}
\begin{rSubsection}{Land Processing Distributed Active Archive Center (LP DAAC), USGS}{\normalfont September 2020 -- June 2023}{Software Engineer I}{}
 \item {\normalfont Designed solutions by identifying client pain points and collaborating with scientists with more efficient goal achievement in the ASTER mission.}
  \item {\normalfont Conducted updates on 100+ outdated libraries within several programming languages by applying cutting edge and best engineering methodologies, ensuring 12 different enterprise-level applications were updated and future-proofed.}
 \item {\normalfont Applied Sprint methodology to help with organization of active tasks while transitioning to sAFE methodology for more efficient project management in the future.}
 \item {\normalfont Identified and resolved issues in ASTER tools by surveying bug reports and feature suggestions to effectively design user-centered tools without disrupting productivity.}
 \item {\normalfont Coordinated with NASA scientists in requirements gathering for the creation of 150+ Jira tickets for new features and further maintenance of ASTER tools.}
\end{rSubsection}
\begin{rSubsection}{EROS CalVal Center of Excellence, USGS}{\normalfont June 2020 -- September 2020}{Software Engineer Intern.}{}
 \item {\normalfont Research for georeferencing design using Landsat 8 data to attach a geographical coordinate system to an aerial image for georeferencing automation development.}
 \item {\normalfont Designed an algorithm with Python scripting and the ArcGIS API for automated production of georeferenced images.}
  \item {\normalfont Create weekly presentations to present progress of development with tasks to aim for in the upcoming week.}
\end{rSubsection}

\end{rSection}

%============Projects==========
\begin{rSection}{Projects}
\begin{rSubsection}{LP DAAC External Website}{\normalfont September 2020 -- June 2023}{Software Engineer}{\href{https://lpdaac.usgs.gov}{https://lpdaac.usgs.gov}}{}
  \item{\normalfont Proactively contributed to the development of new features and played a pivotal role in the continuous maintenance of a high-traffic website, serving over 200,000 monthly visitors.}
  \item{\normalfont Collaborated in a 4 person team to improve the user experience for LPDAAC scientists to create news articles, ASTER Products, and E-Learning pages.}
  \item{\normalfont Identified recurring breakdown issues in the publications table, leading to a comprehensive overhaul that optimized data-scraping. Achieved a substantial reduction in loading times, ensuring consistent and efficient data access.}
  \item{\normalfont Initiated the creation of the podcasts page by manipulating Django to interface with Wagtail CMS. Allowing visitors another resource for obtaining information on different NASA missions such as ECOSTRESS and EMIT.}
\end{rSubsection}

\end{rSection}

%===========Education==========

\begin{rSection}{Education}
{\bf South Dakota State University, Brookings, SD} \hfill {\normalfont August 2017 -- May 2021} 
\\ {\normalfont B.E., Computer Science with Minors in Mathematics and Software Engineering}\hfill 
\end{rSection}

%========Technical Abilities=======

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: \ & {\normalfont C, C++, C\#, Python, HTML5, CSS, Javascript, PHP, Perl}  \\
Frameworks: &  {\normalfont Django, Flask, ASP.Net MVC, Wagtail CMS}\\
Tools: & {\normalfont Docker, Kubernetes, Jira, Acunetix } \\
Databases: & {\normalfont PostgresSQL}\\
Cloud Technologies: & {\normalfont AWS}\\
Version Control: & {\normalfont Git}\\
\end{tabular}
\end{rSection}

%========Technical Abilities=======
\begin{rSection}{Awards}
\begin{rSubsection}{}{}{}{}
    \item {Graduated university with Magna Cum Laude distinction: \normalfont2021} \\
    \item {Deans list for 5 semesters.}
\end{rSubsection}

\end{rSection}


\end{document}


